CIS 673 Project Report

### 2020-04-15 report/draft.tex
Write more on the last writer wins register

We started by encoding the state as is (a value $x$ of any type $X$
and a timestamp $t$ of type $Int$) and by encoding the $assign$ effect
by only requiring as a precondition that $t' \neq t$, in order to
enforce timestamp uniqueness. \TODO{Finish this}

%% Servois quickly retuned the following
%% counterexample:

%% \[
%% x_1 \neq x_2 \wedge t_1 = t_2 \wedge t
%% \]

>>>>

We started by encoding the state as is (a value $x$ of any type $X$
and a timestamp $t$ of type $Int$) and by encoding the $assign$ effect
by only requiring as a precondition that $t' \neq t$, in order to
enforce timestamp uniqueness. Servois quickly retuned the following
counterexample:

\[
t_1' = t \vee t_2' = t
\]

\TODO{Gautam: Do you understand why exactly does this fail? It is in
  line 36,37 of lwwreg.yml} Servois found that if one of the effect
timestamps $t_1', t_2'$ is equal to the initial timestamp $t$, then
executing them in different orders will lead to one of them not
satisfying the precondition once, but satisfying it in the other
run. However, this behaviour is disallowed by the LWW specification
since all new timestamps $t'$ are unique.

In order to deal with that, we extended the state to keep a set of all
seen timestamps, and we modified the precondition to require that
\TODO{Finish this.}
